\chapter{Beef and Pork Mains}
\begin{comment} % chatper intro
  Naturally, all of these are delicious.
  Need I say more?
  % say something about when to use lean meats, I guess
\end{comment}

\recipe[]{Beef-Stuffed Bell Peppers}
\serves{4}
\preptime{15 minutes}
\cooktime{40 minutes}
\freezerfriendly
\begin{ingreds}
  4 red bell peppers, seeded with tops and membranes removed
  1 tbsp olive oil, plus extra for greasing the peppers
  1 lb extra-lean ground beef
  1 sweet onion, chopped
  1 cup mushrooms, chopped
  2 tsp minced garlic
  1 cup shredded spinach
  1 cup cooked quinoa
  salt and pepper
\end{ingreds}
\begin{method}[Preheat oven to \ftemp{350}.]
  Rub pepper with olive oil and place them
  hollow side down in baking pan.

  Bake the peppers for 10 minutes, until slightly softened,
  and remove them from the oven.
  Flip them hollow side up and set aside.

  Heat the olive oil in a large skillet over
  medium-high heat.

  Add the ground beef and saut\'e for about 10 minutes,
  until it is cooked through.
  Stir in the onion, mushrooms, and garlic and saut\'e
  for about 6 minutes, until translucent.

  Remove the skillet from the heat and stir in
  the spinach and quinoa.
  Season the filling with salt and pepper.

  Spoon the filling into the red peppers
  and return the baking dish to the oven.
  Bake 15 minutes and serve.
\end{method}
\begin{tips}
  Peppers can be packed in freezer bags and frozen
  after filling.
  Just thaw them in the refrigerator
  and bake for 20-25 minutes at \ftemp{350}.
\end{tips}

\recipe[Excellent served on taco boats or in a bowl with tortilla chips on the side.]{Chili}
\serves{8}
\freezerfriendly
\preptime{15 minutes}
\cooktime{2.5 hours}
\begin{ingreds}
  1 \nicefrac{1}{2} lb ground beef
  2 garlic buds, minced
  1 large onion, chopped
  1 tbsp butter
  1 tsp ground cumin
  2 tsp chili powder
  1 tsp paprika
  1 \nicefrac{1}{2} tsp crushed red pepper
  1 (10 oz) can tomato sauce
  2 large cans red kidney beans
  2 large cans black beans
  2 cans whole kernel corn, drained
\end{ingreds}

\begin{method}
  Saut\'e ground beef, onion, and garlic in butter.
  Add other ingredients and cook slowly for at least 2 hours.
\end{method}

\begin{comment}		%
\recipe[]{Red Beans and Rice*}
\serves{}
\freezerfriendly
\preptime{}
\cooktime{}
\begin{ingreds}

\end{ingreds}

\begin{method}

\end{method}

\end{comment}		%

\recipe[Beef jerky with a hint of root beer and chipotle.]{Root Beer Jerky}

\begin{ingreds}
  3 cups root beer
  \nicefrac{1}{3} cup soy sauce
  1 tsp chipotle powder
  1 tsp paprika
  1 tsp granulated garlic
  \nicefrac{1}{4} tsp liquid hickory smoke
  1 lb London broil strips, or other lean beef strips
\end{ingreds}

\begin{method}
  Mix all ingredients except the meat into a saucepan
  and heat over medium-high heat.
  Cook until the mixture reduces by half, 15 to 20 minutes.
  Remove from the heat and let cool completely.

  Pour the marinade into a 1-gallon resealable plastic
  freezer bag and add the meat strips to the marinade.
  Mix the strips around so they get completely coated with the marinade.

  Remove as much air as possible from the bag,
  seal, and place it in the refrigerator for 4 hours.
  During the marinating time, remove the bag
  from the refrigerator and work the meat around
  so the marinade is fully incorporated into it.

  Remove the strips from the marinade and arrrange
  in a single layer in a dehydrator.
  Dry at \ftemp{158} for 4-6 hours, or until done
  (jerky is dark and bends without snapping).
\end{method}

\recipe[Use pre-cut stew meat to save prep time on this Asian-inspired dish.]{Slow Cooker Beef and Broccoli}
\serves{4-6}
%\preptime{}
\cooktime{4.5 hours}
\begin{ingreds}
  1 lb beef stew meat
  1 cup beef broth
  \nicefrac{1}{2} cup soy sauce
  1 tbsp sesame oil
  4 cloves garlic, minced
  \nicefrac{1}{4} cup brown sugar
  1 large head of broccoli, cut into pieces
  \nicefrac{1}{4} cup water
  \nicefrac{1}{4} cup cornstarch
\end{ingreds}

\begin{method}
  Combine broth, soy sauce, sesame oil, garlic,
  and brown sugar in a slow cooker.
  Mix well and cook on low for 4 hours.

  Mix cornstarch and water in a small bowl.
  Add to slow cooker with broccoli pieces, stirring.
  Cook on low for another 30 minutes.

  Serve over rice.
\end{method}
