\chapter{Chicken and Turkey Mains}

\recipe[]{Mushroom Chicken Thighs*}
\serves{4}
\preptime{10 minutes}
\cooktime{45 minutes}
\begin{ingreds}
  3 tbsp olive oil
  4 cups sliced wild mushrooms
  2 tsp minced garlic
  1 tsp fresh thyme, chopped
  4 (6-oz) bone-in chicken thighs
  salt and pepper
\end{ingreds}
\begin{method}[Preheat oven to \ftemp{425}.]
  Heat 2 tbsp olive oil in a large ovenproof skillet
  over medium-high heat.

  Add the mushrooms and saut\'e for 10 minutes,
  until golden brown and lightly caramelized.

  Add the garlic and thyme and saut\'e 2 minutes more.

  Return the skillet to heat
  and add the remaining olive oil.

  Season the chicken thighs with salt and pepper.

  Pan sear the chicken until lightly browned
  on both sides, about 10 minutes.

  Place the skillet into the oven and roast
  until the chicken is cooked through, 20 to 25 minutes.

  Serve the chicken with a generous spoonful of
  saut\'eed mushrooms.
\end{method}

\recipe[Served atop jasmine rice and green beans.]{Sweet-As-Honey Chicken}
\serves{2}
\preptime{5 minutes}
\cooktime{30 minutes}
\begin{ingreds}
  1 tbsp vegetable oil
  1 tsp minced garlic
  1 lime, cut into wedges
  1 thumb ginger, peeled and minced
  \nicefrac{1}{2} cup jasmine rice
  2 chicken breasts, 6 oz each
  1 \nicefrac{1}{2} tbsp white wine vinegar
  1 tbsp soy sauce
  1 pouch chicken stock concentrate
  1 oz honey
  6 oz green beans
  salt and pepper
\end{ingreds}
\begin{method}
  Bring 1 cup water and a pinch of salt
  to a boil in a small pot.
  Once water boils, add rice to pot.
  Cover, lower heat, and reduce to a gentle simmer.
  Cook until tender, about 15 minutes.

  Meanwhile, heat a drizzle of oil in a large pan
  over medium-high heat.
  Season chicken all over with salt and pepper.
  Add to pan and cook until no longer pink
  in the center, about 4-5 minutes per side.
  Remove from pan and set aside.

  Reduce heat under pan to medium-low
  and add a drizzle of oil.
  Saut\'e minced ginger and garlic until
  softened and fragrant, about 1 minute.
  Pour in vinegar and let reduce
  until almost dry and evaporated.

  Stir soy sauce, 2 tbsp water, stock concentrate,
  and honey into same pan.
  Let simmer until mixture thickens to
  a glaze-like consistency, 2-3 minutes.
  Remove from heat, then return chicken to pan
  and toss to coat.
  Set aside.

  Place green beans in a medium, microwave-safe bowl
  with a splash of water.
  Cover bowl with plastic wrap and poke
  a few holes in wrap.
  Microwave on high until just tender, about 2 minutes.
  Meanwhile, heat a drizzle of oil in a medium pan
  over medium-high heat.
  Thoroughly drain green beans, then add to pan.
  Cook, tossing occasionally, until lightly crisped, 3-5 minutes.
  Season with salt, pepper, and a squeeze of lime.

  Divide rice between plates;
  top with green beans and chicken.
  Serve with remaining lime wedges on the side for squeezing over.
\end{method}



\recipe[Tasty vegetable-filled turkey burgers.]{Tender Turkey Burgers}
\freezerfriendly
\serves{4}
\cooktime[Bake time]{30 minutes}
\preptime{15 minutes}
\begin{ingreds}
  2 tsp olive oil
  \nicefrac{1}{2} sweet onion, chopped
  \nicefrac{1}{2} red bell pepper, chopped
  1 celery stalk, finely chopped
  2 tsp minced garlic
  1 \nicefrac{1}{2} lb ground turkey
  dash sea salt
  dash freshly ground black pepper
  \columnbreak
  Olive oil spray
  4 sprouted grain buns
  Boston lettuce leaves, for garnish (optional)
  Red onion, thinly sliced, for garnish (optional)
  Tomato, sliced, for garnish (optional)
\end{ingreds}

\begin{method}[Preheat the oven to \ftemp{400}.]
  Heat the olive oil in a medium skillet over medium-high heat.
  Add the onion, red bell pepper, celery, and garlic
  and saut\'e until softened, about 4 minutes.

  Transfer the cooked vegetables to a medium bowl
  and add the turkey, salt, and pepper.
  Mix the ingredients together and divide the
  turkey mixture into four portions.

  Shape the portions into four patties about
  \nicefrac{3}{4} inch thick.
  Line a baking dish with parchment and place
  the turkey burgers on the dish in one layer.
  Lightly spray the patties with olive oil.

  Bake the burgers until they are golden and
  cooked through, about 25 minutes.
  Serve the burgers on buns topped with lettuce,
  onion, and tomato.
\end{method}

\begin{tips}
  Patties can be kept in the freezer --
  just put some parchment paper between them
  before wrapping them up.

  \medskip
  Also, don't be afraid to spread some of the veggies
  around the baking tray before putting it into the oven.
\end{tips}
