\chapter{Desserts and Drinks}
\begin{comment}
Meal planning isn't easy, so don't forget
to reward yourself with one (or more) of these desserts
and refreshing drinks.
\end{comment}

\recipe[Very easy to make -- you may even have all of the ingredients already.]{Banana Bread}
\vegetarian
%\serves{}
\preptime{15 minutes}
\cooktime[Bake time]{45 minutes}
\begin{ingreds}
  4 very ripe bananas, peeled
  \nicefrac{1}{3} cup melted butter
  1 tsp baking soda
  pinch of salt
  \nicefrac{3}{4} cup sugar
  1 large egg, beaten
  1 tsp vanilla extract
  1 \nicefrac{1}{2} cups all-purpose flour
  1 tsp cinnamon
  crushed pecans
\end{ingreds}

\begin{method}[Preheat oven to \ftemp{350} and butter the baking pan.]
  In a mixing bowl, mash the ripe bananas with
  a fork until completely smooth.
  Stir the melted butter into the mashed bananas.

  Mix in the baking soda and salt.
  Stir in the sugar, beaten egg, vanilla extract, and cinnamon.
  Mix in the flour and any additions.

  Pour the batter into the prepared pan,
  and sprinkle crushed pecans atop the batter.
  Bake for 45 minutes, or until a tester inserted
  into the center comes out clean.

  Remove from the oven and cool completely on a rack.
  Remove the banana bread from the pan and serve.
\end{method}
\begin{tips}
  Rather than chopping pecans manually (it'll take a while),
  wrap them in a paper towel and use the side of
  a flat knife to crush them.
\end{tips}

\recipe[An easy way to make cookies out of any cake mix.]{Cakies}
\vegetarian
%\preptime{}
\cooktime[Bake time]{10 minutes}
\begin{ingreds}
  1 box cake mix
  2 eggs
  \nicefrac{1}{2} cup vegetable oil
  nuts or fruit (optional)
\end{ingreds}
\begin{method}[Preheat oven to \ftemp{375}.]
  Mix all ingredients together and roll into walnut-sized balls.

  Place 2 inches apart on ungreased cookie sheet.

  Bake 8--10 minutes.
  Remove and cool for 2 minutes.
\end{method}

\recipe[Can be made with regular or almond milk.]{Chai Tea Latte*}
\serves{1}
\begin{ingreds}
  2 chai tea bags
  \nicefrac{1}{4} cup boiling water
  \nicefrac{3}{4} cup milk
  honey or sugar to taste (optional)
  cinnamon or nutmeg, for garnish (optional)
\end{ingreds}
\begin{method}
  Steep the tea bags in the hot water
  for 3 to 5 minutes.

  Warm milk in a pan, then whisk with a frother.
  Combine the milk and tea,
  adding honey or sugar as desired.
  Sprinkle with cinnamon or nutmeg and serve.
\end{method}

\recipe[]{Creamy Pecan Pralines}
\serves{18 pcs.}
\begin{ingreds}
  1 cup granulated sugar
  1 cup (packed) light brown sugar
  2 tablespoons light corn syrup
  2 tablespoons butter
  Pinch of salt
  1/2 cup sweetened condensed milk
  1 teaspoon vanilla extract
  1 1/2 cups pecan pieces
\end{ingreds}
\begin{method}
  Combine the sugar, brown sugar, corn syrup, butter, salt,
  and condensed milk in a heavy saucepan over medium heat.

  With a wooden spoon, stir until the sugar dissolves.
  Continue to cook, stirring, until smooth and light brown,
  about 8 minutes.

  Add the vanilla and pecans and continue to cook,
  stirring, until the mixture reaches \ftemp{234} to
  \ftemp{240} on a candy thermometer or the soft ball stage,
  that is, when a bit dropped into cold water
  forms a soft ball that flattens.

  Remove from the heat and drop by the spoonful onto wax paper.
  Let cool.

  Remove from the paper with a thin knife.
  Pralines can be stored in an airtight container
  at room temperature for up to 2 weeks.
\end{method}
\begin{tips}
  If you attempt to roast the pecans yourself,
  be sure to check them frequently!
  They can and \emph{will} catch fire if left unattended
  (we know from experience).
\end{tips}

\recipe[]{Easy Penuche*}
\preptime{5 minutes}
\cooktime{10 minutes}
\serves{90 pcs.}
\begin{ingreds}
  1 cup unsalted butter
  2 cups brown sugar, packed
  \nicefrac{1}{2} cup whole milk
  1 tsp vanilla extract
  3 \nicefrac{1}{2} to 4 cups sifted powdered sugar
  1 \nicefrac{1}{2} cups coarsely chopped pecans
\end{ingreds}
\begin{method}
  Spray a 9x5" loaf pan with cooking spray
  and line with parchment paper.
  Set aside.

  Melt butter in a heavy-bottomed 2-quart saucepan
  over \linebreak medium-low heat, stirring as needed.
  Stir in the brown sugar and cook for
  2 minutes, stirring constantly.

  Gently pour in the milk and, stirring constantly,
  bring mixture to a boil.
  Remove from heat and let cool for 30-40 minutes,
  or until mixture is lukewarm or room temperature.

  Stir in the vanilla extract.
  Stir in powdered sugar, 1 to \nicefrac{1}{2} cup
  at a time, stirring until completely combined.
  Add powdered sugar just until the mixture is
  thick and has the consistency of fudge.

  Stir in pecans, then spoon into the prepared
  loaf pan and top with additional pecans if desired.
  Cover and cool until firm.

  Cut into squares and store in the refrigerator
  in an airtight container.
\end{method}

\recipe[Add an equal amount of unsweetened black tea for an extra refreshing drink.]{Lemonade}
%\serves{}
%\preptime{}
%\cooktime{}
\vegan
\begin{ingreds}
  1 \nicefrac{3}{4} cups white sugar
  8 cups water
  1 \nicefrac{1}{2} cups lemon juice
\end{ingreds}

\begin{method}
  In a small saucepan, combine sugar and 1 cup water.
  Bring to a boil and stir to dissolve sugar.
  Allow to cool to room temperature, then cover
  and refrigerate until chilled.

  Remove seeds from lemon juice, leaving pulp (if applicable).
  In pitcher, stir together chilled syrup, lemon juice,
  and remaining 7 cups water.
\end{method}
\begin{tips}
  If you don't want (or have time) to wait
  for the syrup to chill slowly,
  add ice to it instead.
\end{tips}

\recipe[]{Microwave Mug Brownie*}
\serves{1}
\preptime{6 minutes}
\cooktime{1 minutes}
\begin{ingreds}
  2 tbsp melted butter or oil
  2 tbsp water, milk, or chocolate milk
  \nicefrac{1}{4} tsp vanilla extract
  dash salt
  2 tbsp white sugar
  2 tbsp unsweetened cocoa powder
  4 tbsp flour
\end{ingreds}
\begin{method}
  In a coffee mug, add water/milk
  melted butter/oil, a dash of salt,
  and vanilla extract. Whisk well.

  Add cocoa powder, sugar, and flour,
  whisking well after each.

  Microwave for 60 seconds.
  Center should be slightly molten.
  Do not overcook.

  Enjoy with a spoon.
\end{method}

\recipe[Can be used as a fruit dip or eaten by itself.]{Sweet Potato Dip}
\serves{2 \nicefrac{1}{2} cups}
\preptime{10 minutes}
\cooktime{30 minutes}
\freezerfriendly
\vegetarian%?
\begin{ingreds}
  2 cups sweet potato, cooked and pur\'eed
  \nicefrac{1}{2} cup vanilla yogurt
  1 tbsp raw honey
  1 tsp pure vanilla extract
  \nicefrac{1}{4} tsp ground cinnamon
  \nicefrac{1}{8} tsp ground nutmeg
  \nicefrac{1}{8} tsp ground ginger
  dash ground allspice
  fruit, for dipping (optional)
\end{ingreds}
\begin{method}
  In a medium bowl, whisk together
  the sweet potato, honey, vanilla,
  and seasonings until well blended.

  Serve with cut up fruit, if desired.

  Store any extra in a sealed container.
\end{method}
\begin{tips}
  If you don't want to cook the potatoes yourself,
  you can use two thawed frozen sweet potato patties.
\end{tips}
