\chapter{Soups and Pasta Sauces}
\begin{comment}
Pasta is cheap, and soups can be prepared
in rather large batches --
perfect when you're on a college student budget (we are).
\end{comment}

\recipe[This recipe takes a while, so start it in the morning and leave it to cook all day.]{Bean Soup}
\serves{6}
\freezerfriendly
\cooktime{8 hours}
\preptime{20 minutes}
\begin{ingreds}
  1 bag 15 bean soup mix
  1 (32 oz) box chicken broth
  water
  1 ham bone with meat
  1 package Conecuh sausage
  1 onion, chopped
\end{ingreds}

\begin{method}
  Saut\'e sausage and onion until sausage
  is cooked and onion is soft.

  Place ham bone, sausage, and beans into slow cooker.
  Cover with chicken broth and water.
  Add half of the seasoning package from the soup mix bag and mix well.

  Cook on low for 8 hours.
\end{method}

\recipe[Easily improvised, this recipe serves as a nice base upon which to build.]{Chicken Soup}
\serves{}
\preptime{}
\cooktime{}
\freezerfriendly
\begin{ingreds}
  1 lb chicken breasts, cooked (may be shredded or chopped)
  1 tbsp butter
  2 stalks celery, chopped
  1 cup carrots, shredded
  1 package egg noodles
  4 (14.5 oz) cans chicken broth
  1 (14.5 oz) can vegetable broth
  \nicefrac{1}{2} tsp basil
  \nicefrac{1}{2} tsp oregano
  salt and pepper to taste
\end{ingreds}

\begin{method}
  In a large pot over medium heat, melt butter.
  Cook vegetables in butter until just tender, about 5 minutes.

  Pour in broth and stir in other ingredients.
  Boil, then reduce heat and simmer for 20 minutes before serving.
\end{method}

\recipe[Thick and creamy, this clam chowder pairs well with cold days.]{Clam Chowder}
\serves{6-8}
\preptime{15 minutes}
\cooktime{35 minutes}
\freezerfriendly
\begin{ingreds}
  \nicefrac{1}{2} lb thick cut bacon
  6 small cans chopped clams
  4 bottles clam juice
  6-8 red potatoes, diced
  2 cups heavy cream or half and half
  3 tbsp cornstarch
  1 stalk fresh rosemary, chopped finely
  1 medium onion, diced
  salt, pepper, garlic to taste
\end{ingreds}

\begin{method}
  In a large saucepan, boil potatoes until soft.

  Cut bacon into \nicefrac{1}{2} inch pieces,
  place in large stockpot, and fry until crispy.
  Remove bacon from pot onto paper towel.
  Drain grease from pot, leaving enough to layer the bottom.

  Cook onion in stockpot until soft.
  Add clams, clam juice, and spices into stock pot;
  cook on medium-high heat until warm.

  Pour heavy cream into lidded cup and add cornstarch.
  Shake well, then add to stockpot.
  Stir until liquid begins to thicken.

  Add potatoes to stockpot and simmer about 10-20 minutes.
  Add bacon to chowder or use as a garnish when serving.
\end{method}

\recipe[Basic spaghetti sauce. A great way to put some extra veggies on a plate.]{Spaghetti Sauce}
%\serves{}
\freezerfriendly
%\preptime{}
%\cooktime{}
\begin{ingreds}
  1 lb ground beef
  1 lb ground Italian sausage
  2 cups carrots, shredded
  1 zucchini, shredded
  1 yellow squash, shredded
  1 can olives, chopped
  2 tsp garlic, minced
  1 package mushrooms, finely chopped
  \columnbreak
  1 large onion, chopped
  3 (14 oz) cans pasta sauce
  Italian seasoning
  crushed red pepper
  chili powder
  cajun seasoning
  salt and pepper to taste
\end{ingreds}

\begin{method}
  In a large pot, brown meat with onion and garlic; drain.
  Return to heat and add carrots, zucchini, squash,
  mushrooms, and olives, cooking until vegetables are tender.

  Stir in pasta sauce one can at a time; season to taste.
  Reduce heat to low and simmer until uniformly heated,
  then remove from heat.

  Serve over noodles.
\end{method}
\begin{tips}
  If you're feeling adventurous, try serving
  over spaghetti squash instead of pasta.
  % anything special to do to it first?
\end{tips}
